### 2017-05-23 Docs/managing_jobs/managingjobs.tex

  gfortran 6.1.1 is used for nightly regression testing.

@@

The scripts {\tt vis-titan.run} and {\tt parallel-yt-new} in that
same directorywill manage the \yt jobs by calling a
python script for each file that matches a pattern.  
Note that the actual visualization command itself is launched by
{\tt parallel-yt-new}, again using the {\tt aprun} command.  But
{\tt aprun} can only launch a single job at a time, so this means
we cannot easily do (trivally) parallel visualization on a node.  For
this reason, running on rhea is preferred.

>>>>

\item {\em gfortran 6.2}: These compilers work without any known issues.

  gfortran 6.2.1 is used for nightly regression testing.

@@

The scripts {\tt vis-titan.run} and {\tt parallel-yt-new} in that
same directorywill manage the \yt\ jobs by calling a
python script for each file that matches a pattern.  
Note that the actual visualization command itself is launched by
{\tt parallel-yt-new}, again using the {\tt aprun} command.  But
{\tt aprun} can only launch a single job at a time, so this means
we cannot easily do (trivally) parallel visualization on a node.  For
this reason, running on rhea is preferred.
